---
title: "Plotting_mc_simulation"
author: "Christoph Voelter"
date: "January 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(gridExtra)
library(ggpubr)
library(corrr)
library(tidyr)

```



##First mistake in search sequence depending on different memory size simulations

```{r loading data, include = FALSE}

updating.sim6 <- read.table(file="Updating_children simulation_6boxes.txt", header=T, sep="\t") %>%
  filter(!is.na(no.error))

updating.sim7 <- read.table(file="Updating_children simulation_7boxes.txt", header=T, sep="\t") %>%
  filter(!is.na(no.error))

updating.sim8 <- read.table(file="Updating_children simulation_8boxes.txt", header=T, sep="\t") %>%
  filter(!is.na(no.error))



```

```{r include=FALSE}
#from wide to long format


# The arguments to gather():
# - data: Data object
# - key: Name of new key column (made from names of data columns)
# - value: Name of new value column
# - ...: Names of source columns that contain values
# - factor_key: Treat the new key column as a factor (instead of character vector)
updating.sim6_long <- gather(updating.sim6, position, error, X2nd:no.error, factor_key=TRUE)

updating.sim7_long <- gather(updating.sim7, position, error, X2nd:no.error, factor_key=TRUE)
updating.sim7_long 

updating.sim8_long <- gather(updating.sim8, position, error, X2nd:no.error, factor_key=TRUE)



```


### Six Boxes  

```{r echo=FALSE}
updating.sim6[1:7] 

ggplot(data = updating.sim6_long , aes(x = X, y = error, fill = position)) +  labs(x = NULL, y = "Probability to committ an error",
				 fill = "Error position")+
		  geom_bar(stat = "identity", position = position_dodge()) +scale_y_continuous(expand = c(0,0))  +
		  coord_cartesian(ylim = c(0, 1)) +
		 # geom_vline(xintercept = 2.5, colour="white")+
		 geom_segment(aes(x = 6.5, y = -0.13,  xend=6.5, yend = 0), colour = "black", size=0.5)+

		 # Use grey scale
		scale_fill_grey(start=0.9, end=0.1) + theme_classic()+
		  theme(plot.margin = unit(c(1, 1, 4, 1), "lines"))

	 
	
```

####First mistake in sequence (average value) 
No error coded as "7"

* MS0 simulation: 3.77373
* MS1 simulation: 4.4913 
* MS2 simulation: 5.2258
* MS3 simulation: 5.8727
* MS4 simulation: 6.5045  
* MS5 simulation: 7
 
### Seven Boxes  

```{r echo=FALSE}
updating.sim7[1:8] 
ggplot(data = updating.sim7_long , aes(x = X, y = error, fill = position)) +  labs(x = NULL, y = "Probability to committ an error",
				 fill = "Error position")+
		  geom_bar(stat = "identity", position = position_dodge()) +scale_y_continuous(expand = c(0,0))  +
		  coord_cartesian(ylim = c(0, 1)) +
		 # geom_vline(xintercept = 2.5, colour="white")+
		 geom_segment(aes(x = 6.5, y = -0.13,  xend=6.5, yend = 0), colour = "black", size=0.5)+

		 # Use grey scale
		scale_fill_grey(start=0.9, end=0.1) + theme_classic()+
		  theme(plot.margin = unit(c(1, 1, 4, 1), "lines"))

	 
	
```
####First mistake in sequence (average value) 
No error coded as "8"

* MS0 simulation: 4.01756
* MS1 simulation: 4.7766 
* MS2 simulation: 5.532  
* MS3 simulation: 6.2162  
* MS4 simulation: 6.8819 
* MS5 simulation: 7.4995 
* MS6 simulation: 8  


### Eight Boxes    

```{r echo=FALSE}
updating.sim8[1:9] 
ggplot(data = updating.sim8_long , aes(x = X, y = error, fill = position)) +  labs(x = NULL, y = "Probability to committ an error",
				 fill = "Error position")+
		  geom_bar(stat = "identity", position = position_dodge()) +scale_y_continuous(expand = c(0,0))  +
		  coord_cartesian(ylim = c(0, 1)) +
		 # geom_vline(xintercept = 2.5, colour="white")+
		 geom_segment(aes(x = 6.5, y = -0.13,  xend=6.5, yend = 0), colour = "black", size=0.5)+

		 # Use grey scale
		scale_fill_grey(start=0.9, end=0.1) + theme_classic()+
		  theme(plot.margin = unit(c(1, 1, 4, 1), "lines"))

	 
	
```

####First mistake in sequence (average value) 
No error coded as "9"

* MS0 simulation: 4.24982  
* MS1 simulation: 5.0271  
* MS2 simulation: 5.7821  
* MS3 simulation: 6.5262  
* MS4 simulation: 7.2156  
* MS5 simulation: 7.8956  
* MS6 simulation: 8.5023  
* MS7 simulation: 9  
